The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-23 paper.tex
update

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the disk and atmosphere is in pressure equilibrium,\
  we can write the steady-state gaseous density distributions,\
  confined in the total potential, of disk and the Galactic atmosphere as\
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is the proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and the atmosphere on the mid-plane $z=0$.

  We tabulate all parameters in \Cref{table-parameters}, except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.\

  The initial density profile based on the above construction is shown in \Cref{density-profile}\
  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\

@@

  A crucial component in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
  the log-normal probability distribution with mean $\mu$ and dispersion $\sigma$,\
  %the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu$ and dispersion $\sigma$,\
  and the power-law Kolmogorov spectrum
  \begin{equation}
    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-\beta},
  \end{equation}
  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.\
  The spectrum $D(k)$ with a power law index $\beta$ in the Fourier space has a cutoff wave number $k_{\text{min}}=375.0$,\
  corresponding to the average clump sizes of $\sim 20$ pc.\
  \Cref{table-parameters} presents the parameters of clumpy disk and their references.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                             & Description                               & Value                                & Reference                       \\ \midrule
{\bf ISM Disk }                                       &                                           &                                      &                                 \\
$z_{0}$                                               & Scale height of disk                      & 100 pc                               & \citet{peak-ism-density}        \\
$T_{\text{\text{disk}}}$                              & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}          \\
$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}          \\
$T_{\text{\text{c}}}$                                 & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   & \multicolumn{1}{c}{''}          \\
$k_{\text{min}}$                                      & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}          \\
$\mu$                                                 & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
$\sigma$                                              & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 & \multicolumn{1}{c}{''}          \\
$\beta$                                               & Power law index                           & -5/3                                 & \multicolumn{1}{c}{''}          \\ \hline
{\bf Atmosphere }                                     &                                           &                                      &                                 \\
$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere                 & $10^{6}$ K                           & \citet{temperature-MW}          \\ \hline
{\bf Static stellar potential }                       &                                           &                                      &                                 \\
$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citet{velocity-dispersion-MW}  \\
$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &                                 \\ \hline
{\bf Static dark halo potential }                     &                                           &                                      &                                 \\
$v_{\text{halo}}$                                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citet{Johnston1995}            \\
$d_{\text{h}}$                                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}          \\ \midrule
\end{tabular}
\end{table*}

>>>>

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the isothermal disk and atmosphere is in pressure equilibrium,\
  we can write the steady-state gaseous density distributions,\
  confined in the total potential, of the disk and the Galactic atmosphere as\
  \begin{subequations}
  \begin{align}
     \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disk-density}\\
     \text{, if $|z| < z_{0}$}& \nonumber \\
     \nonumber\\
     \displaystyle \rho_{\text{atmp}}(z) = \rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right]&\label{isothermal-atmp-density}\\
     \text{, otherwise,}& \nonumber
  \end{align}
  \label{disk-atm-sys}
  \end{subequations}
  where $m_{\text{p}}$ is the proton mass,\
  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disk and atmosphere,\
  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and atmosphere on the mid-plane $z=0$.

  We tabulate parameters in the \textbf{Isothermal disk} and \textbf{Atmosphere}\
  categories in \Cref{table-parameters},\
  except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\

  The initial density profile of \Cref{disk-atm-sys} is shown in \Cref{density-profile}\
  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\

@@

  A crucial component in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The spatial density distribution $\rho_{\text{clumpy}}(\bold{x})$ of clumpy disk obeys\
  the log-normal probability distribution\
  %the log-normal probability distribution \citep{Berkhuijsen2008}\
  with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
  and the power-law Kolmogorov spectrum
  \begin{equation}
    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{\rho}(k)$ is the Fourier transform of $\rho_{\text{clumpy}}(\bold{x})$.\
  The spectrum $D(k)$ in the Fourier space is characterized by the power law index $\beta$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual cloud $\sim 20$ pc.\

  The temperature in each cell of the clumpy disk is determined by $p_{\text{disk}}$

  We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.

@@

  \begin{enumerate}
     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(\bold{x})$ by \Cref{isothermal-disk-density}.
     \item Using PyFC code to obtain the clumpy cuboid $\rho_{\text{clumpy}}$ obeying\
           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
     \item $\rho_{\text{ismDisk}}(\bf{x}) = \rho_{\text{clumpy}}(\bf{x}) \times \rho_{\text{isoDisk}}(\bf{x})$.
     \item
  \end{enumerate}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                             & Description                               & Value                                & Reference                       \\ \midrule
{\bf Isothermal disk }                                &                                           &                                      &                                 \\
$z_{0}$                                               & Scale height of disk                      & 100 pc                               & \citet{peak-ism-density}        \\
$T_{\text{\text{isoDisk}}}$                           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}          \\
$\rho_{\text{isoDisk}}^{\text{peak}}$                 & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}          \\ \hline
{\bf Atmosphere }                                     &                                           &                                      &                                 \\
$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere                 & $10^{6}$ K                           & \citet{temperature-MW}          \\ \hline
{\bf Clumpy disk }                                    &                                           &                                      &                                 \\
$T_{\text{\text{c}}}$                                 & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   & \multicolumn{1}{c}{''}          \\
$k_{\text{min}}$                                      & Cutoff wave number                        & 375.0                                & \multicolumn{1}{c}{''}          \\
$\mu_{\text{clumpy}}$                                 & Mean of number density                    & 1.0 $\text{cm}^{-3}$                 & \citet{Wagner2012}              \\
$\sigma_{\text{clumpy}}$                              & Dispersion of number density              & 1.7 $\text{cm}^{-3}$                 & \multicolumn{1}{c}{''}          \\
$\beta$                                               & Power law index                           & -5/3                                 & \multicolumn{1}{c}{''}          \\ \hline
{\bf Static stellar potential }                       &                                           &                                      &                                 \\
$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citet{velocity-dispersion-MW}  \\
$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &                                 \\ \hline
{\bf Static dark halo potential }                     &                                           &                                      &                                 \\
$v_{\text{halo}}$                                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citet{Johnston1995}            \\
$d_{\text{h}}$                                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}          \\ \midrule
\end{tabular}
\end{table*}
